%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CV Template for Econ PhDs (used by Prerna Kundu)
%
% This template is based on the CV template created by Rishi Shah (available on the Overleaf website), with changes made to suit an econ/policy background

% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.35in,top=0.6in,right=0.35in,bottom=0.3in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
	pdftitle={Hridayam Kapila CV},
}

\name{Hridayam Kapila} % Your name
\address{(+91) 8595539366 \\ \href{mailto:kapilahridayam@gmail.com}{kapilahridayam@gmail.com} \\ \href{https://www.linkedin.com/in/hridayam-kapila-323987266/}{LinkedIn}} %create a custom url on LinkedIn to insert here

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%    EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Education}
		
		\textbf{Aryabhatta College, University of Delhi} \hfill \textit{2026}
		\\ Bachelor’s Degree in Economics, Minor in Mathematics
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%    RESEARCH INTERESTS SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Research Interests}
		Environmental Economics, Ecological Economics, Climate Change, Applied Microeconomics, Applied Econometrics.
	\end{rSection}
	
	%--------------------------------------------------------------------------------
	%   Work Experience
	%-----------------------------------------------------------------------------------------------
	\begin{rSection}{Work Experience}
		
		\textbf{Mutual Funds Distributor (Self-Employed),} Delhi, India \hfill \textit{May 2024 - Present} \\
		Advise clients on mutual fund investments based on financial goals \& risk assessment.
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%    Projects Section
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Academic Papers and Projects}
		
		\textbf{Undergraduate Thesis:} \textit{Carbon Emissions in Africa: EKC and Regional Integration} \\
		This study aims to understand whether a long-term co-integrating relationship exists between Regional Integration and Carbon Emissions, while also testing for Environmental Kuznets Curve for our sample of nine countries for the period 2006 to 2022.
		
		%Project 1
		\textbf{VAR Modeling of Macroeconomic Data (R)} (\href{https://github.com/HKay111/Macroeconomic-Analysis-R}{GitHub})\\
		Modeled short-run dynamics between exchange rate, inflation, \& output gap using a Vector Autoregression (VAR) model with robust inference. This is strictly a coding exercise and may have mistakes.
		
		%Project 2
		\textbf{Econometric Analysis of INR Exchange Rate (R)} (\href{https://github.com/HKay111/IGD-Project}{GitHub})\\
		Investigated CPI \& Output Gap impact on INR exchange rate using R time series models; analyzed policy implications.
		
		%Project 3
		\textbf{Music Data Exporter (Python)} (\href{https://github.com/HKay111}{GitHub})\\
		Developed Python script using Last.fm API for automated music data extraction, processing, \& export.
		
		%Project 4
		\textbf{QS Rankings Analysis (Tableau)} (\href{https://public.tableau.com/app/profile/hridayam.kapila/vizzes}{Tableau Public})\\
		Created interactive Tableau dashboard visualizing \& analyzing university ranking data.
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%    Positions of Responsibilities
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Positions of Responsibility}
		\textbf{Co-Founder \& VP, Placement Unit (Economics Dept.), Aryabhatta College}
		\hfill \textit{Sept 2025 - Apr 2026} \vspace{2pt}\\
		Establishing and leading the unit to connect economics students with internship and career opportunities.
		
		\textbf{Advisory, Mind Over Matter (Economics Society), Aryabhatta College}
		\hfill \textit{Aug 2025 - Apr 2026} \vspace{2pt}\\
		Provide strategic guidance and mentorship to the current editorial board.
		
		\textbf{Editor-in-Chief, Mind Over Matter (Economics Society), Aryabhatta College}
		\hfill \textit{Oct 2024 - Aug 2025} \vspace{2pt}\\
		Led the editorial team, managing content strategy, publication processes, and project communications.
		
		\textbf{Social Media Manager, Arahata (B.A. Programme Society), Aryabhatta College}
		\hfill \textit{Nov 2024 - May 2025} \vspace{2pt}\\
		Manage society's online presence \& communication strategies to enhance outreach \& engagement.
		
		\textbf{Treasurer, Arahata (B.A. Programme Society), Aryabhatta College}
		\hfill \textit{Oct 2023 - Oct 2024} \vspace{2pt}\\
		Managed society finances: budget planning, fund allocation, expense tracking, \& financial records. 
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%    Skills and Languages 
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Skills}
		\textbf{Languages:} Hindi (Native), English (Fluent) \\
		\textbf{Technical Skills:} R, STATA, Tableau, LaTeX, Git/GitHub, Excel. \\
	\end{rSection}
	
	
\end{document}
